\textbf{Learning semi-Markovian DAGs with flow-based VAE}

### 2023-12-04 Tex/paper.tex
tex

Firstly, we set the proportion of bidirectional edges to 0.5 and compared the performance of our method with that of DAG-GNN. The results, as depicted in Figure \ref*{SHD_FDR_prop50}, demonstrate that our method surpasses DAG-GNN in terms of both SHD and FDR. Notably, with a node size of 20, our method exhibits stable training, resulting in a significant difference in SHD and FDR. Figure \ref*{example_graphs} presents the estimated graphs produced by each method. The graph estimated by DAG-GNN (third column) contains considerably more edges than the true graph (first column), whereas the graph estimated by our method (second column) has a number of edges much closer to that of the true graph.

\begin{figure}[H]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/SHD_dependence_50.pdf}
        \caption{SHD with dependence proportion 0.5}
        \label{SHD_prop50}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/FDR_dependence_50.pdf}
        \caption{FDR with dependence proportion 0.5}
        \label{FDR_prop50}
    \end{subfigure}
    \caption{SHD and FDR with dependence proportion 0.5}
    \label{SHD_FDR_prop50}
\end{figure}

>>>>

Firstly, we set the proportion of bidirectional edges to 0.5 and compared the performance of our method with that of DAG-GNN. The results, as depicted in Figure \ref*{SHD_FDR_prop30}, demonstrate that our method surpasses DAG-GNN in terms of both SHD and FDR. Notably, with a node size of 20, our method exhibits stable training, resulting in a significant difference in SHD and FDR. Figure \ref*{example_graphs} presents the estimated graphs produced by each method. The graph estimated by DAG-GNN (third column) contains considerably more edges than the true graph (first column), whereas the graph estimated by our method (second column) has a number of edges much closer to that of the true graph.

\begin{figure}
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/SHD_dependence_30_DAG_threshold0.3.pdf}
        \caption{SHD with dependence proportion 0.3}
        \label{SHD_prop30}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/FDR_dependence_30_DAG_threshold0.3.pdf}
        \caption{FDR with dependence proportion 0.3}
        \label{FDR_prop30}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/Predicted Edges_dependence_30_DAG_threshold0.3.pdf}
        \caption{Number of predicted edges}
        \label{pred_edge_prop30}
    \end{subfigure}
    \caption{SHD, FDR, and number of predicted edges with dependence proportion 0.3}
    \label{SHD_FDR_prop30}
\end{figure}
